% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
\usepackage{enumitem,amssymb}
\usepackage{amsmath} 
\usepackage{booktabs}

\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
\usepackage{hyperref}
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
\usepackage{color}
\renewcommand\UrlFont{\color{blue}\rmfamily}
% \urlstyle{rm}
%

\input{reviewing}

\begin{document}
%
\title{Benchmarking User-Specific Link Traversal Query Optimization: Evidence-Based Simulation of Decentralized Query Patterns } 
\rt{Since this is a resource paper, I'd recommend giving your benchmark/simulator a name. Maybe some word-play around users and SolidBench. U-SolidBench? MySolidBench? SolidBenchU? ... A title could then become something in the form of "SolidBenchU: Evidence-Based Simulation Benchmark for User-Specific Queries within Decentralized Environments"}
\author{Ruben Eschauzier\inst{1}\orcidID{0000-0002-6475-806X} \and
Ruben Taelman\inst{1}\orcidID{0000-0001-5118-256X}}

\institute{Department of Electronics and Information Systems, Ghent University – imec}
\titlerunning{Revisiting Link Prioritization for Efficient Traversal}

%
% \authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
% \email{lncs@springer.com}\\
% \url{http://www.springer.com/gp/computer-science/lncs} \and
% ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
% Context:      Why the need is so pressing or important
Optimizing queries in decentralized environments, 
where data sources are often unknown and dynamically discovered, 
remains a major challenge due to the lack of prior knowledge about data distribution and availability.
\rt{I would add one sentence here (or otherwise incorporate it above) to motivate the need for user-specific client-side query engines. Something like: Client-side apps can reuse the same client-side query engine, which introduces optimization opportunities.}
% Need:         Why something needed to be done at all
User-specific client-side query engines can mitigate this limitation by exploiting patterns in previously issued queries.
However, existing benchmarks fail to accurately reflect the performance \rt{Not sure "performance" is the right word here. I would talk about the typical properties and characteristics of user-specificness, or something like that, which then can lead to better performance.} of such approaches,
as they typically rely on repetitive or template-based query structures that lack realistic variability.
Moreover, publicly available query logs from real decentralized applications are scarce or absent in the literature.
Consequently, the evaluation of client-side decentralized query optimization techniques remains incomplete and cannot be performed under representative conditions.
% Task:         What was undertaken to address the need
To fill this gap, we introduce an evidence-based simulation of client query usage patterns \rt{... and offer it as a reusable benchmark(?)}.
This simulation \rt{benchmark?} enables systematic evaluation and comparison of client-side optimization techniques under realistic and reproducible conditions.
% Object:       What the present document does or covers
We demonstrate its use by applying it to a novel caching-based link traversal query processing approach.
To assess the impact of realistic query sequences, we compare the results against a benchmark that is not sequence-based, 
highlighting how query sequence simulation influences client-side optimization performance.
% Findings:     What the work done yielded or revealed
We find that [placeholder for results].
% Conclusion:   What the findings mean for the audience
We conclude: [placeholder for conclusion]

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}


\input{sections/introduction.tex}
\input{sections/related-work.tex}
\input{sections/benchmark.tex}
\input{sections/caching.tex}
\input{sections/experiment}
\input{sections/results}

% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\bibliographystyle{splncs04}
\bibliography{references/bib}

\end{document}
