\section{Query Sequence Benchmark}

In this section, we detail our simulation methodology and the resulting hyperparameters.
We base our sequence generator on SolidBench~\cite{taelman2023link}, 
which simulates realistic decentralized social media applications within the Solid ecosystem.
SolidBench utilizes the Social Network Benchmark (SNB) dataset~\cite{erling2015ldbc,angles2020ldbc} 
and applies the Linked Data Benchmark Council (LDBC) choke point methodology~\cite{angles2014linked}.
Its workload combines standard SNB \textit{interactive} queries with custom \textit{discover} templates,
which explicitly target Link Traversal Query Processing (LTQP) choke points in decentralized environments. 

To support sequence-based evaluation, we extend three core components of the SolidBench ecosystem:

\begin{itemize}
    \item \textbf{Query Generator:} We modify the generator to produce correlated query sequences that reflect empirical real-world usage patterns.
    
    \item \textbf{Dataset Generator:} We enhance the data generation process to model interest-based similarities between simulated users.
    
    \item \textbf{Benchmark Runner:} We integrate sequence execution logic into the existing runner to facilitate straightforward, reproducible sequence-based experiments and allow easy generation of default configuration files.
\end{itemize}

\subsection{Simulation Methodology}
Our methodology models three interdependent behaviors: task-oriented logical sessions,
user interests for data locality,
and refinement patterns for iterative query development.

\subsubsection{Logical Query Sessions}
To model logical sessions, we categorize queries into four primary topics: 
person-specific messages, forum information, person attributes, and message attributes. 
Because queries in decentralized environments often depend on preceding results, 
we map the output types of each template to valid subsequent templates. 
This creates a directed graph of query progression that governs the flow of a logical session.
% \rt{If you can't add a figure in the introduction, I'd add one here, to illustrate what you explain in this paragraph.}

Within a session, a template's \emph{instantiation values} are typically derived 
from the previous query's results. 
To realistically simulate this ``click-through'' 
behavior, we execute centralized equivalents of the LDBC SNB queries using 
QLever~\cite{bast2017qlever}. 
We then randomly sample the returned result set 
to instantiate the subsequent query template. 
If a query yields no results, 
we fall back to our default, interest-based instantiation methodology.

Finally, we simulate logical session switching. 
Drawing from web browsing behavior, we assign each sequence a session-switching probability sampled from a log-normal 
distribution with a mean of 15\%~\cite{meiss_whats_2009,schneider2009understanding}. 
During sequence generation, a session switch triggers a random choice with equal probability: the engine either starts a new 
session (using interest-based instantiation) or resumes a previous one (deriving instantiation values from that session's last executed query).
To prevent repetitive queries and maintain a uniform distribution of template instantiations, 
we explicitly prohibit backtracking within our model. 
Additionally, we maintain a balanced template distribution by dynamically 
scaling down each template's selection probability proportionally to its 
overall frequency.


\subsubsection{User Interest Modeling}
\label{ss:userinterests}

Individuals interact more frequently with users sharing similar interests~\cite{mitzlaff2013user}. 
To simulate this behavior, we use the underlying LDBC dataset utilized by SolidBench~\cite{erling2015ldbc}, 
which inherently models realistic user preferences. 
The LDBC generator, Datagen, produces person profiles containing specific interests, 
educational backgrounds, and workplaces. 
It links users based on these demographic and interest overlaps, 
yielding a non-random network topology with a realistic degree distribution.

We use this interest-driven topology to generate template instantiation values 
for the first query of each logical session. 
Specifically, we construct a binary feature vector $v_{k}$ for each user $k$:
$ v_{k} = (x_{k,1}, \dots, x_{k,n}, y_{k,1}, \dots, y_{k,m})$,
where $x_{k,j}=1$ if user $k$ holds stated interest $j$, and $y_{k,l}=1$ 
if user $k$ completed study $l$.

% For each sequence, we randomly select a base person $k$ and compute the cosine similarity 
% between $v_{k}$ and the feature vectors of all other users in the dataset.
% We then select template instantiation values probabilistically based on these 
% similarity scores by applying a softmax function with a temperature parameter $T$:

% \begin{equation}
%    P(c_{i,k}) = \frac{e^{s_i / T}}{\sum_{j=1}^{N} e^{s_j / T}},
% \end{equation}

% where $s_i$ is the similarity score for candidate person $i$.
% To maintain efficiency at large scale factors, we restrict this operation to the top $N$ ranked candidates. 
% For templates requiring non-person values (e.g., posts or activities),
% selection probabilities are derived from the similarity scores of the content's creators.  

%%%%%%%%%%%%
For each sequence, we randomly select a base person $k$ and compute the cosine similarity 
between $v_{k}$ and the feature vectors of all other users.
Let $N$ be the total number of users. To maintain efficiency at large scale factors, 
we restrict our candidate pool to $C_{k,M}$, defined as the set of the top $M < N$ users 
ranked by similarity to $k$. 
Template instantiation values are then selected probabilistically using a softmax function 
with temperature $T$:

\begin{equation}
   P(i \mid k) = \frac{e^{s_{k,i} / T}}{\sum_{u \in C_{k,M}} e^{s_{k,u} / T}},
\end{equation}

where $s_{k,i}$ is the similarity score between base person $k$ and candidate $i \in C_{k,M}$. 
For templates requiring non-person values (e.g., posts or activities),
selection probabilities are derived from the similarity scores of the content's creators.
%%%%%%%%%%%%

\subsubsection{Refinement Patterns}


The benchmark simulates query refinement by randomly applying composable 
transformations to an instantiated query template. 
Following our literature review, we specifically focus on transformations, and their reciprocal counterparts, that
add or modify BGPs, OPTIONALs, UNIONs, and query instantiation values.

% To ensure transformations meaningfully alter query execution rather than superficially appending triples,
% we apply a choke point-based design methodology~\cite{angles2014linked}. 
% The generator sequentially applies refinements to a base SolidSessionBench template.
% By mapping empirical exploratory usage patterns~\cite{arenas2025exploring}, outlined in Section \ref{sec:related_work_qup}, directly to
% planning (P) and traversal (T) choke points, we translate emperical findings to 
% (TODO How to link this description? The idea is to say we map from emperical findings to patterns and challenges that are challenging for engines)
% benchmarking targets.
% These choke points build on the choke points outlined in SolidBench~\cite{taelman2023link,taelman2023evaluation}:

To ensure transformations meaningfully alter query execution rather than superficially appending triples, 
we apply a choke point-based design methodology~\cite{angles2014linked}. 
The generator sequentially applies refinements to a base SolidSessionBench template. 
By mapping the empirical exploratory usage patterns~\cite{arenas2025exploring} outlined in Section~\ref{sec:related_work_qup} 
directly to planning (P) and traversal (T) choke points, 
we translate empirical user behaviors into concrete execution bottlenecks that rigorously test query engines. 
These benchmarking targets expand upon the choke points established in SolidBench~\cite{taelman2023link,taelman2023evaluation}:

\begin{itemize}
\item \textbf{Result Refinement:} Adjusts query selectivity by adding or removing \\\texttt{FILTER} constraints (P.1) and selective triple patterns (P.3).

\item \textbf{Result Generalization:} Expands queried classes by adding new selective (P.3) or non-selective (P.4) triple patterns to existing Basic Graph Patterns (BGPs).

\item \textbf{Result Extension:} Fetches additional attributes by appending triple patterns to BGPs (P.3, P.4), 
or by introducing \texttt{OPTIONAL} and \texttt{UNION} blocks which can alter filter push-down capabilities (P.2).

\item \textbf{Query Refinement:} Further modifies the query structure 
by adding or removing \texttt{OPTIONAL} and \texttt{UNION} blocks (P.2).

\item \textbf{Shifting Query Intent:} Substitutes template instantiation values to start traversal from different seed documents. 
This expands or shifts the reachable sub-web (T.1, T.2).
\end{itemize}

Beyond planning, these refinements also impact traversal.
Specifically, substituting template instantiation values to start traversal from different seed documents,
alongside structural modifications, such as adding new trile patterns, introduces several traversal choke points:
\textbf{T.1} expands or contracts the reachable sub-web through predicate additions;
\textbf{T.2} changes the reachable documents by altering the traversal starting point;
\textbf{T.3} changes the number of hops required to obtain relevant data,
corresponding to SolidBench choke points L.1--L.6~\cite{taelman2023evaluation};
and \textbf{T.4} alters the usability of structural indexes, such as
type indexes, corresponding to SolidBench choke point L.8~\cite{taelman2023evaluation}.


% To ensure these transformations meaningfully alter query execution characteristics, rather 
% than superficially appending triples that maintain a one-to-one relation with the result 
% set, we apply a choke point-based design methodology~\cite{angles2014linked}. 
% Specifically, we define several planning choke points for client-side query 
% optimization in decentralized environments, building on the original SolidBench 
% choke points~\cite{taelman2023link}: 
% \textbf{P.1} involves adding or removing a \texttt{FILTER}, which requires 
% prior knowledge to adjust query plans and estimate selectivity; 
% \textbf{P.2} addresses adding or removing \texttt{UNION} or \texttt{OPTIONAL} 
% clauses to alter filter push-down capabilities; 
% \textbf{P.3} covers adding or removing selective triple patterns; 
% and \textbf{P.4} focuses on adding or removing non-selective triple patterns.

% Beyond planning, these refinements also impact traversal processes. 
% We identify the following traversal choke points: 
% \textbf{T.1} expands or contracts the reachable sub-web through predicate additions; 
% \textbf{T.2} shifts the sub-web by substituting the traversal starting point; 
% \textbf{T.3} changes the number of hops required to obtain relevant data, 
% corresponding to SolidBench choke points L.1--L.6~\cite{taelman2023evaluation}; 
% and \textbf{T.4} alters the usability of structural indexes, such as 
% type indexes, corresponding to SolidBench choke point L.8~\cite{taelman2023evaluation}.

% The generator sequentially applies these refinements to a base SolidSessionBench query template. 
% By default, every refinement pattern includes a reciprocal "undo" operation.
% The supported refinement operators include (1) adding new OPTIONAL and UNION blocks 
% or inserting triples into existing ones (including specific UNION branches);
% (2) adding new triple patterns to existing Basic Graph Patterns (BGPs),
% which define the core graph-matching logic of a SPARQL query;
% (3) appending new query constraints via FILTER statements;
% and (4) substituting template instantiation values to begin traversal from a different seed document.

The generator supports variable instantiation within refinements, allowing users 
to bind pattern variables to specific values randomly selected from candidates provided through configuration files. 
Users can define custom query refinement patterns using JSON files to augment the provided 
default configurations. These defaults, along with documentation and pattern descriptions, 
are available on GitHub: https://github.com/RubenEschauzier/SolidBench.js/tree/feature/\\user-based-query-sequences/templates/refinements.
% \footnote{https://github.com/RubenEschauzier/SolidBench.js/tree/feature/user-based-query-sequences/templates/refinements}

% Through this flexible generator, we explicitly simulate the empirical exploratory usage patterns~\cite{arenas2025exploring} 
% identified in Section~\ref{sec:related_work_qup}.
% We map these empirical patterns directly to our composable query transformations and choke points:
% (1) we simulate result refinement by adding or removing FILTER constraints 
% and selective triple patterns in the BGP to adjust query selectivity (Choke points P.1, P.3);
% (2) we replicate result generalization by adding new triples to existing BGPs 
% (Choke points P.3, P.4);
% (3) we simulate result extension by adding triple patterns to BGPs, OPTIONAL blocks, and UNION blocks (Choke points P.3, P.4, P.2);
% and (4) we model query refinement by adding or removing OPTIONAL and UNION blocks (Choke point P.2).
% Because our refinement rules are fully composable,
% the generator aligns with the empirical observation that these exploratory patterns 
% are not mutually exclusive and frequently co-occur within a single session.

% Through this flexible generator, we explicitly simulate the empirical exploratory 
% usage patterns~\cite{arenas2025exploring} identified in Section~\ref{sec:related_work_qup}. 
% We map these empirical patterns directly to our composable query transformations and 
% choke points:

% \begin{itemize}
%     \item \textbf{Result Refinement:} We simulate this by adding or removing 
%     \texttt{FILTER} constraints and selective triple patterns in the BGP to adjust 
%     query selectivity (Choke points P.1, P.3).
    
%     \item \textbf{Result Generalization:} We replicate this by adding new triples 
%     to existing BGPs (Choke points P.3, P.4), mirroring how users expand queried 
%     classes and fetch related entities.
    
%     \item \textbf{Result Extension:} We simulate this by adding triple patterns 
%     to BGPs, \texttt{OPTIONAL} blocks, and \texttt{UNION} blocks (Choke points P.3, P.4, P.2).
    
%     \item \textbf{Query Refinement:} We model this through the addition or removal 
%     of \texttt{OPTIONAL} and \texttt{UNION} blocks (Choke point P.2).
% \end{itemize}

% As our refinement rules are fully composable, 
% the generator naturally reflects the empirical observation that 
% exploratory patterns are not mutually exclusive and frequently co-occur within a single 
% session.

\subsection{Hyperparameters}

The sequence generation process introduces several new hyperparameters, 
which are detailed in Table~\ref{tab:generation_hyperparameters} together with their default values. 
To guarantee reproducibility despite extensive random sampling, 
a single seeded pseudo-random number generator (PRNG) is used througout the 
entire pipeline.

\begin{table}[htbp]
    \centering
    \caption{LogT-normal distribution parameters ($\mu, \sigma$) control the queries per sequence, 
    queries per logical session, and the probability of switching logical sessions. 
    Refinement parameters define the likelihood (\texttt{patternProbability}) 
    and bounds (\texttt{min/maxRefinementLength}) of generating a refinement sequence for a given query. 
    Instantiation relies on a softmax \texttt{temperature} and a \texttt{maxLogits} 
    cutoff for similarity-based entity selection.}
    \label{tab:generation_hyperparameters}
    \begin{tabular}{l l c}
        \toprule
        \textbf{Category} & \textbf{Parameter} & \textbf{Value} \\
        \midrule
        \textbf{Distributions} ($\mu, \sigma$) 
        & Sequence Length & 3.0, 0.2 \\
        & Session Length & 1.7, 0.5 \\
        & Transition Probability & -2.0, 0.25 \\
        \addlinespace
        \textbf{Refinements} 
        & \texttt{patternProbability} & 0.1 \\
        & \texttt{min/maxRefinementLength} & 2, [3--5] \\
        \addlinespace
        \textbf{Instantiation} 
        & \texttt{temperature} & 0.1 \\
        & \texttt{maxLogits} & 5--10 \\
        \bottomrule
    \end{tabular}
\end{table}
