\section{Caching in Link Traversal-based Query Processing}
% Unlike traditional query engines that evaluate queries against a centralized,
% pre-built index, LTQP evaluates queries directly over the live Web using the ``follow-your-nose'' principle of Linked Data. 
% Execution relies on two core components: a \emph{link queue} and an \emph{active local store}~\cite{taelman2023evaluation,hartig2012sparql}.
% The engine initializes the link queue with seed URIs (often extracted from the query).
% It then iteratively dereferences these URIs, retrieving RDF documents.
% The triples from these documents are deposited into the active local store; a temporary, query-specific,
% in-memory dataset over which the SPARQL operators are actually evaluated. 
% Simultaneously, new URIs are discovered within the retrieved data 
% and added to the link queue according to specific \emph{reachability criterions}~\cite{hartig2009executing},
% which dictate which links are relevant to follow based on the query structure.
% Furthermore, to reduce memory usage, 
% engines like Comunica~\cite{taelman2018comunica} typically employ \emph{dictionary encoding} within the local store,
% converting lengthy string-based URIs and literals into compact integer identifiers.

% Hartig~\cite{hartig2011caching} originally established the fundamental concept of caching within this paradigm,
% demonstrating that keeping a local repository of recently accessed Web documents mitigates
% the high network latency inherent to LTQP.

% To validate the SolidSessionBench query sequences, 
% we integrated three \\caching approaches into Comunica~\cite{taelman2018comunica,taelman2023link}. 
% As Comunica is JavaScript-based, 
% its event loop handles traversal and local query execution as interleaved, 
% asynchronous processes.
% The caching approaches cache the triples from documents dereferenced during link traversal in-memory.
% High cache hit rates eliminate redundant HTTP requests, increasing traversal speed and reducing query latency. 
% To evaluate how different cache management strategies impact this latency,
% we compare the following three configurations:

% \paragraph{Unindexed Cache}
% This baseline approach caches the triples obtained during traversal.
% Upon a cache hit, these quads are retrieved and indexed into the active local store for query execution.
% In essence, this approach caches an array of triples, with associated metadata for each source.

% \paragraph{Indexed Cache}
% Alternatively, we index triples before caching them. 
% Upon a cache hit, the engine extracts only the triples that match the query's triple patterns. 
% This approach reduces the local store's memory footprint and indexing overhead for two reasons:
% dictionary encoding compresses the data, and pre-filtering ensures fewer triples enter the local store. 
% While this increases the initial cache ingestion cost, we hypothesize the trade-off is positive given sufficiently high hit rates.

% \paragraph{Indexed Cache + Cardinality estimation}
% As the cache is indexed, it can execute count queries to estimate quad pattern cardinalities.
% Traditional LTQP relies on zero-knowledge heuristics due to a lack of prior knowledge~\cite{hartig2011zero}.
% By estimating cardinalities against \emph{all} cached documents,
% regardless of their reachability for the current query,
% we can replace these heuristics with Comunica's default cost-based optimizer~\cite{taelman2018comunica}
% to generate more accurate query plans. \\

% % \rt{It may be helpful for the reader to visually represent these 3 approaches next to each other.}

% For each caching approach, we investigate three sizes of in-memory cache: small (350,000 quads), medium (700,000 quads),
% and large (1,400,000 triples). These triple counts correspond to about 10\%, 20\%, and 40\% of the total
% generated dataset size.

% Our implementations adhere to the RFC-9111 specification~\cite{fielding2022rfc}, 
% meaning the cache correctly interprets standard HTTP headers (like Cache-Control)
% to determine how long to store data, just like a web browser.
% However, because the benchmark dataset is static, cache entries require no revalidation and never become stale. 
% Consequently, the observed hit rates are likely higher than in a live environment. 
% Furthermore, while the fundamental concept of caching in link traversal is established~\cite{hartig2011caching}
% integrating and comparing these distinct caching strategies provides novel and strong baselines
% for evaluating caching in traversal engines, upon which future research
% into advanced caching approach can build.

Unlike traditional query engines that evaluate queries against a centralized, pre-built index, 
LTQP evaluates queries directly over the live Web~\cite{taelman2023evaluation,hartig2012sparql} 
using the ``follow-your-nose'' principle. 

Starting from a seed URI (often extracted from the query), 
the engine fetches data via a \emph{link queue} (governed by \emph{reachability criteria}~\cite{hartig2009executing}) 
and deposits the retrieved triples into an \emph{active local store}. 
This local store is an in-memory dataset over which the query executes, 
typically utilizing dictionary encoding~\cite{taelman2018comunica}. 

Previous work~\cite{hartig2011caching} established the fundamental concept of caching within this paradigm,
demonstrating that a local repository of recently accessed Web documents 
mitigates the high network latency inherent to LTQP.


For our experiments, we use the Comunica LTQP engine~\cite{taelman2018comunica,taelman2023link}. 
As a \\JavaScript-based engine, it relies on the event loop to asynchronously interleave traversal and local query execution. 
To validate the SolidSessionBench sequences, we integrated three caching approaches into this architecture. 
These approaches cache dereferenced triples in-memory to reduce latency, and we evaluate their impact by comparing three configurations:


\paragraph{Unindexed Cache}
This baseline approach caches raw arrays of triples alongside source metadata. 
Upon a cache hit, the engine retrieves and indexes these triples into the active local store.

\paragraph{Indexed Cache}
This approach pre-indexes triples before caching. 
Upon a hit, the engine extracts only triples matching the query's patterns. 
This pre-filtering, combined with dictionary encoding, reduces local store memory and indexing overhead, 
potentially offsetting the higher initial ingestion costs.

\paragraph{Indexed Cache + Cardinality Estimation}
This configuration leverages the indexed cache to estimate quad pattern cardinalities 
across \emph{all} cached documents. 
This replaces traditional zero-knowledge heuristics~\cite{hartig2011zero} 
with Comunica's cost-based optimizer~\cite{taelman2018comunica} to generate more accurate query plans.

We evaluate three cache capacities: small (350k quads, $\sim$10\% of the dataset), 
medium (700k, $\sim$20\%), and large (1.4M, $\sim$40\%). 

Our implementations adhere to the RFC-9111 specification~\cite{fielding2022rfc}, 
meaning the cache correctly interprets standard HTTP headers (e.g., Cache-Control) 
just like a web browser would. 
However, because the benchmark dataset is static, cache entries require no revalidation and never become stale. 
Consequently, observed hit rates are likely higher than in a live environment. 

Ultimately, comparing these strategies establishes strong baselines 
for caching performance in realistic user-centric environments, 
upon which future research into advanced caching approaches can build.